Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-21 latex/article.tex
notations

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widely investigated since the
seminal Marching-Cubes approach by Lorensen and
Cline~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by Lengyel \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs.  However, it
was developed to visualize in real-time static or near static data and
present a complex CPU implementation.  In this paper we propose a GPU
pipeline inspired from this method.  It leaves the CPU free for other
tasks and avoids synchronisation with the GPU.  Our high framerate
also allows this method to run in real-time on fully dynamic data.
The triangulation is controlled by a GPU LoD criterion that ensures
that triangles project onto more than one pixel, thus removing
geometrical aliasing.

@@

\sloppy In our context, we consider digital shapes (any subset of $\Z^d$) and
boundaries of digital shapes. We denote by $\DSh$ the Gauss
digitization of $\Shape$ in a $d-$dimensional grid with grid step $h$,
\emph{i.e.}  $\DSh = \Shape \cap (h\Z)^d$. For such digitized set
$\DigShape$, $\partial\Body{\DigShape}{h}$ denotes its
topological boundary, seen as a cellular Cartesian complex (See
Fig. \ref{fig:notations}-b). It is thus composed of $0$-cells and
$1$-cells (resp. \emph{pointels} and \emph{linels}), and, for $d=3$,
with $2$-cells ({\em surfels}), embedded in the digital grid.

>>>>

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widely investigated since the
seminal Marching-Cubes approach by Lorensen and
Cline~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by Lengyel \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs.  However, it
was developed to visualize in real-time static or near static data and
present a complex CPU implementation.\todo{DC: rajouter une phrase par
  rapport à lengyel, Helene ? JP?}  In this paper we propose a GPU
pipeline inspired from this method.  It leaves the CPU free for other
tasks and avoids synchronization with the GPU.  Our high framerate
also allows this method to run in real-time on fully dynamic data.
The triangulation is controlled by a GPU LoD criterion that ensures
that triangles project onto more than one pixel, thus removing
geometrical aliasing.

@@

\sloppy In our context, we consider digital shapes (any subset of $\Z^d$) and
boundaries of digital shapes. We denote by $\DSh$ the Gauss
digitization of $\Shape$ in a $d-$dimensional grid with grid step $h$,
\emph{i.e.}  $\DSh = \Shape \cap (h\Z)^d$. For such digitized set
$\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset of $\R^d$ corresponding
to the union of hypercubes centered at $h\cdot \vz$ for  $\vz\in Z$
with edge length $h$. By doing so, both $\partial\Shape$ and
$\partial\Body{Z}{h}$ are topological boundary of objects lying in the
same space (See
Fig. \ref{fig:notations}-b). Note that the combinatorial digital boundary
of $Z$ made of cells in a cellular Cartesian complex (\emph{pointels},
\emph{linels}, {\em surfels}, \ldots), can be trivally embedded into $\R^d$
such that it coincides with $\partial\Body{Z}{h}$.
